%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{mmynayak-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Mrunmayee}{Nayak}{ \urlstyle{same}\href{https://www.linkedin.com/in/mmnayak/}{mmynayak@linkedin.com}\\
\href{address:Bhubaneswar,India}{Bhubaneswar,India}| 884.789.4773 | \href{mailto:mmynayak@gmail.com}{mmynayak@gmail.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{KIIT university | India}
\location{Master in Computer Application}
\descript{2021-current | CGPA : 8.24}
\sectionsep

\subsection{Shailabala college}
\descript{BSc in Computer Science}
\location{Aug 2021 | Cuttack}
\location{ Cum. GPA: 6.84 / 10.0 \\
Major GPA: 7.07 / 10.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Masters}
Programming and Data structures \\
Operating System \\
Database Management System \\
Discrete Mathematics \\
Cloud Computing \\
Computer Networks \\
Object-oriented programming \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}

\location{Languages:-}
\textbullet{} Advance:- Java \\  \textbullet{} Intermediate:- Python \\ \textbullet{} Novice:- Javascript, C  \\
\sectionsep
\location{Tools and IDEs :-}
\textbullet{} Visual Studio \textbullet{} Oracle Database with 10g expression \textbullet{} Linux \textbullet{} Windows \textbullet{} Git \\
\sectionsep
\location{Technologies :-}
\textbullet{} CSS \textbullet{} HTML5 \textbullet{} MySql \\
\sectionsep
\subsection{Soft Skills}
\textbullet{} Time-Management \textbullet{} Problem-solving \textbullet{}Public speaking  \textbullet{}Versatile \textbullet{}Teamwork \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Language
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages}
\location{Advance:- English, Hindi, Bengali}
\location{Intermediate:- Korean}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Interests
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
\location{Space Exploration}
\location{Revolutionize search}
\location{Writing articles/journals}
\location{Photography}
\location{Learning Multiple Languages}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Resume Objective
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbullet\location{Strong in design and integration with intuitive problem-solving skills.}
\textbullet\location{Proficient in JAVA, PYTHON, JAVASCRIPT, and MySQL.}
\textbullet\location{Looking to start the career as an entry-level software developer with a reputed firm driven by technology.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Project}
\runsubsection{E-LIBRARY}
\descript{| Frontend/Backend }
\location{12/2019 - 04/2020 | Shailabala women's college, Cuttack}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed, designed, deployed and maintained a
network of federated sources that store electronic
documents of various kinds.
\item This digital library acts as a mediator and access to all
shareable documents by library users and handle
information at a massive scale. 
\item Tools/Technology used- \location {HTML,bootstrap,java
script,Visual studio code}
\item \location{ \href{https://in.docworkspace.com/d/sIPzuzcqWAeGC2Y8G}{E-LIBRARY - Project Report}}
\end{tightemize}
\sectionsep

\runsubsection{CORPORATE MAILING SYSTEM}
\descript{| Frontend }
\location{06/2021 - 11/2021 | Shailabala women's college,Cuttack}
\begin{tightemize}
\item Designed and developed a large scale system design of
mailing service that lets you compose mail and send it
to a respective selected object.
\item A corporate mailing system can help process physical
mail, manage e-mail, and even archive the data.
\item Technology used - \location {HTML,CSS,JAVASCRIPT,MYSQL}
\item \location{ \href{https://in.docworkspace.com/d/sIKHuzcqWAf6GyY8G}{CORPORATE MAILING SYSTEM - Project Report}}
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Frontend/Backend Developer}
\descript{| Freelance}
\location{DEC 2021 – current | REMOTE}
\begin{tightemize}
 \item Built flexible code, Application Programming and
libraries for future use.
\item Managed Web Applications and efficient SQL queries
and data transport.
\item Developed server-side logic in Python and JavaScript
Programming language.
\end{tightemize}
\sectionsep
\runsubsection{Content Editor}
\descript{| Koo App }
\location{FEB 2022 – APR 2022 |  Bhubaneswar}
\begin{tightemize}
 \item Created content marketing campaigns to drive leads
and subscribers Use SEO best practices to generate
traffic to the site securely.
\item  Regularly produced various content types by
Information retrieval, including email, social media
posts, and blogs. Managed over 200 profiles per day.
\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievement} 
\location{Certification}
\begin{tightemize}
\item Getting Started with AWS Machine Learning (Coursera) -
Amazon Web Services | MAR-2022 |
\location{ \href{https://www.coursera.org/account/accomplishments/certificate/XTQJCXPTNVFC}{AWS Training and Certification}}
\item Google Cloud Fundamentals for AWS Professionals
(Coursera) - Google | APR-2022 |
\location{ \href{https://www.coursera.org/account/accomplishments/certificate/UKVYQ6CVDPSA}{Google cloud Training and Certification}}
\item Problem Solving Using Computational Thinking
(Coursera) - University of Michigan | MAR-2022 |
\location{ \href{https://www.coursera.org/account/accomplishments/certificate/CDE2UH7YTPR2}{problem-solving training and Certification}}

\end{tightemize}
\sectionsep

\location{Academic}
\begin{tightemize}
\item Secured 1st position in BSc 5th semester for
presenting a seminar on IPAD.
\item 2nd in school in class XII examination 67.8 %
\item 1st in school in class X examination 82.7 %
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
